\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 pwarel.tex
.

The abstraction of the hybrid dynamical system is a a
paritioning of the hybrid state space $\HybridStates$ into hyper-rectangles or cells $C_i \in \Cells$. The cells are
pairwise disjoint $C_i \cap C_j \neq \emptyset$ iff $i \neq j$ and
their union $\bigcup_{C_i\in\Cells}C_i$ is the state space $\HybridStates$. The paritions over
the continuous state space are implicitly defined using a quantization
function $Q_\epsilon$ parameterized by the precision $\epsilon$.
This further defines an equivalence relations such that $(\vx_i)
\equiv (\vx_j) \;\text{iff}\; Q_\epsilon(\vx_i) = Q_\epsilon(\vx_j)$.
In other words, $(\vx_i) \in C_i \; \text{iff} \; C_i = Q_\epsilon(\vx_i)$.

>>>>

The abstraction of the hybrid dynamical system is a a
partitioning of the hybrid state space $\HybridStates$ into hyper-rectangles or cells $C_i \in \Cells$. The cells are
pairwise disjoint $C_i \cap C_j \neq \emptyset$ iff $i \neq j$ and
their union $\bigcup_{C_i\in\Cells}C_i$ is the state space $\HybridStates$. The partitions over
the continuous state space are implicitly defined using a quantization
function $Q_\epsilon$ parameterized by the precision $\epsilon$.
This further defines an equivalence relations such that $(\vx_i)
\equiv (\vx_j) \;\text{iff}\; Q_\epsilon(\vx_i) = Q_\epsilon(\vx_j)$.
In other words, $(\vx_i) \in C_i \; \text{iff} \; C_i = Q_\epsilon(\vx_i)$.
